Responsive or Responsible? The Reputational Cost of Political Compromises

### 2021-11-10 report/figures/table_descriptives.tex
add draft

<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Variables </th>
   <th style="text-align:right;"> Mean Value </th>
   <th style="text-align:right;"> St. Dev </th>
   <th style="text-align:right;"> Min. Value </th>
   <th style="text-align:right;"> Max. Value </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Far Right Party ID </td>
   <td style="text-align:right;"> 0.10 </td>
   <td style="text-align:right;"> 0.30 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Employment </td>
   <td style="text-align:right;"> 4.18 </td>
   <td style="text-align:right;"> 3.85 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 11 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Income </td>
   <td style="text-align:right;"> 6.94 </td>
   <td style="text-align:right;"> 2.64 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 13 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Ethnic Conception </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> National Identity </td>
   <td style="text-align:right;"> 3.63 </td>
   <td style="text-align:right;"> 0.90 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Knowledge </td>
   <td style="text-align:right;"> 1.47 </td>
   <td style="text-align:right;"> 0.82 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 3 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 2 </td>
   <td style="text-align:right;"> 4.32 </td>
   <td style="text-align:right;"> 1.17 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 3 </td>
   <td style="text-align:right;"> 4.84 </td>
   <td style="text-align:right;"> 0.97 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 4 </td>
   <td style="text-align:right;"> 4.55 </td>
   <td style="text-align:right;"> 0.99 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Interest </td>
   <td style="text-align:right;"> 2.93 </td>
   <td style="text-align:right;"> 1.09 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ideology </td>
   <td style="text-align:right;"> 4.75 </td>
   <td style="text-align:right;"> 1.79 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
</tbody>
</table>

>>>>

<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Variables </th>
   <th style="text-align:right;"> Mean Value </th>
   <th style="text-align:right;"> St. Dev </th>
   <th style="text-align:right;"> Min. Value </th>
   <th style="text-align:right;"> Max. Value </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Far Right Party ID </td>
   <td style="text-align:right;"> 0.10 </td>
   <td style="text-align:right;"> 0.30 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Employment </td>
   <td style="text-align:right;"> 4.18 </td>
   <td style="text-align:right;"> 3.85 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 11 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Income </td>
   <td style="text-align:right;"> 6.94 </td>
   <td style="text-align:right;"> 2.64 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 13 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Ethnic Conception </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> National Identity </td>
   <td style="text-align:right;"> 3.63 </td>
   <td style="text-align:right;"> 0.90 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Knowledge </td>
   <td style="text-align:right;"> 1.47 </td>
   <td style="text-align:right;"> 0.82 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 3 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 2 </td>
   <td style="text-align:right;"> 3.32 </td>
   <td style="text-align:right;"> 1.17 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 3 </td>
   <td style="text-align:right;"> 3.84 </td>
   <td style="text-align:right;"> 0.97 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 4 </td>
   <td style="text-align:right;"> 3.55 </td>
   <td style="text-align:right;"> 0.99 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Interest </td>
   <td style="text-align:right;"> 2.93 </td>
   <td style="text-align:right;"> 1.09 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ideology </td>
   <td style="text-align:right;"> 4.75 </td>
   <td style="text-align:right;"> 1.79 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
</tbody>
</table>
